Stochastic Wind Power Forecasting

### 2020-02-10 LaTeX_code/paper/paper_1line.tex
Added initial guess plot in paper, corrected other plots.

\usepackage{graphicx}
\usepackage{amssymb, amsmath}
\usepackage{bm} % more powerful version to get bold
\usepackage{siunitx}

\usepackage{xcolor}

\usepackage{authblk}

@@

\begin{figure}
  \includegraphics[width=120mm,scale=1]{plots/1.png}
  \caption{Installed wind and solar power over the years. We recall the importance of accurate forecasts to use green energies optimally. {\color{red} We still have to ensure that the source is trustworthy (Renzo will do it)}. Redo the figure as well}
\end{figure}Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
\begin{itemize}
\item Allocation of energy reserves such as water levels in dams or oil, and gas reserves.
\item Operation scheduling of controlable power plants.
\item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity service providers (ESPs), Independent power producers (IPPs), and energy traders.
\item Maintenance planning such as that of power plants components and transmission lines.

@@

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/5.eps}
  \includegraphics[width=60mm,scale=1]{plots/245.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/661.eps}
  \includegraphics[width=60mm,scale=1]{plots/805.eps}
  \caption{Four samples from the Uruguayan data of 2019. Each sample compromises of two 24-hour paths. In blue is an hourly wind power production forecast. In orange is the actual wind power production recorded in 10 minute intervals.}
  \label{fig:sample_data}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP_6.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP_6.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP_6.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP_6.eps}
  \caption{We see that forecast errors exhibit skewness, which is exaggerated as a consequence of curtailing in the production. Low power is when produced power is in $[0,0.3]$, mid-power is when it is in $(0.3,0.6]$, and high power when it is in $(0.6,1]$. We have a total of 363 days to use.}
  \label{fig:data_curtailing}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP.eps}
  \caption{We observe that skewness has been reduced after removing the days with curtailing. We have a total of 255 days with no curtailing.}
  \label{fig:data_after_clean}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP_t.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP_t.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP_t.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP_t.eps}
  \caption{Transitions in error between forecast and real production. We can observe that they are not totally centered around zero.}
  \label{fig:error_transitions}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP_t_LP.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP_t_LP.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP_t_LP.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP_t_LP.eps}
  \caption{Transitions after the Lamperti transform. The transitions now present a normal Gaussian shape. This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
  \label{fig:LP_transitions}
\end{figure}
%---END SECTION 1---

@@

\subsection{Optimization}
{\color{red} Rewrite the discussion to obtain fast initial estimate for the two unknow parameters.}

@@

\begin{equation}
 \arg\min \sum\limits_{j}^M \sum\limits_i^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2 ,
 \end{equation}

@@

\begin{equation}
\theta_0 \alpha = \frac{1}{M\Delta t} \sum\limits_j^M \frac{ \sum\limits_i^N (x_{i+1,j}  - x_{i,j})^2}{2 \sum\limits_i^N x_{i,j}(1-x_{i,j}) } \,.
\end{equation}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Model   &  parameters $(\theta_0, \alpha,\delta)$   & AIC & BIC \\ \hline
Model 1 &  $(\add,\add) $    &  \add   &  \add   \\ \hline
Model 2 &   $(1.2,0.1,0.6)$   &  \add   &   \add    \\ \hline
\end{tabular}
\caption{We compare the different models based on information criterion. \add }
\label{tab:model_comparison}
\end{table}
%---END SECTION 5---

%---BEGIN SECTION 6---
\section{Forecast Provider Comparison} \label{Section_6}
We compare forecasts from two different companies for the same period.
\begin{table}
\centering
\begin{tabular}{|c|l|c|c|}
\hline
Forecast Provider & parameters $(\theta_0, \alpha,\delta)$ & AIC & BIC \\ \hline
Provider A  &  $(\add,\add)$      &  \add   & \add    \\ \hline
Provider B  & $(\add,\add) $  &  \add   &   \add  \\ \hline
\end{tabular}
\caption{\add}
\label{tab:forcast_comparison}
\end{table}
In Figure (\add)-(\add), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.

 \begin{table}[h]
 \centering
 \begin{tabular}{|c|l|c|c|}
 \hline
 Model & parameters $(\theta_0, \alpha)$  \\ \hline
 \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}               &  $(\add,\add) \pm (\add,\add)$   \\ \hline
 \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &  $(\add,\add) \pm (\add,\add)$      \\ \hline
 \end{tabular}
 \caption{ \add confidence interval obtained using bootstrap}
 \label{tab:freq_comparison}
 \end{table}
%---END SECTION 6---

@@

@@

    \begin{figure}[h]
        \includegraphics[width=60mm,scale=1]{plots/paths_testing_days/1.eps}
  \includegraphics[width=60mm,scale=1]{plots/paths_testing_days/2.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/paths_testing_days/3.eps}
  \includegraphics[width=60mm,scale=1]{plots/paths_testing_days/4.eps}
      \caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Forecast is from Uruguay pertaining to  year 2019.}
    \end{figure}

    \begin{figure}[h]
      \includegraphics[width=60mm,scale=1]{plots/bands_testing_days/1.eps}
  \includegraphics[width=60mm,scale=1]{plots/bands_testing_days/2.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/bands_testing_days/3.eps}
  \includegraphics[width=60mm,scale=1]{plots/bands_testing_days/4.eps}
       \caption{{\color{red}Pending add legend and choose better colors.}We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Actual production plotted in retrospect. Forecast and data is from Uruguay pertaining to  year 2019.}
    \end{figure}
%---END SECTION 7---

>>>>

\usepackage{graphicx}
\usepackage{amssymb, amsmath}
\usepackage{bm} % more powerful version to get bold
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{authblk}

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{plots/wind_and_solar/plot_over_years.eps}
\caption{Installed wind and solar power over the years \cite{sultana2017review}. We recall the importance of accurate forecasts to use green energies optimally.}
\end{figure}

Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
\begin{itemize}
\item Allocation of energy reserves such as water levels in dams or oil, and gas reserves.
\item Operation scheduling of controlable power plants.
\item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity service providers (ESPs), Independent power producers (IPPs), and energy traders.
\item Maintenance planning such as that of power plants components and transmission lines.

@@

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{plots/5.eps}
\includegraphics[width=0.45\textwidth]{plots/245.eps}\\
\includegraphics[width=0.45\textwidth]{plots/661.eps}
\includegraphics[width=0.45\textwidth]{plots/805.eps}
\caption{Four samples from the Uruguayan data of 2019. Each sample compromises of two 24-hour paths. In blue is an hourly wind power production forecast. In orange is the actual wind power production recorded in 10 minute intervals.}
  \label{fig:sample_data}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{plots/LP_6.eps}
\includegraphics[width=0.45\textwidth]{plots/MP_6.eps}\\
\includegraphics[width=0.45\textwidth]{plots/HP_6.eps}
\includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
\caption{We see that forecast errors exhibit skewness, which is exaggerated as a consequence of curtailing in the production. Low power is when produced power is in $[0,0.3]$, mid-power is when it is in $(0.3,0.6]$, and high power when it is in $(0.6,1]$. We have a total of 363 days to use.}
  \label{fig:data_curtailing}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{plots/LP.eps}
\includegraphics[width=0.45\textwidth]{plots/MP.eps}\\
\includegraphics[width=0.45\textwidth]{plots/HP.eps}
\includegraphics[width=0.45\textwidth]{plots/AP.eps}
\caption{We observe that skewness has been reduced after removing the days with curtailing. We have a total of 255 days with no curtailing.}
  \label{fig:data_after_clean}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{plots/LP_t.eps}
\includegraphics[width=0.45\textwidth]{plots/MP_t.eps}\\
\includegraphics[width=0.45\textwidth]{plots/HP_t.eps}
\includegraphics[width=0.45\textwidth]{plots/AP_t.eps}
\caption{Transitions in error between forecast and real production. We can observe that they are not totally centered around zero.}
\label{fig:error_transitions}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{plots/LP_t_LP.eps}
\includegraphics[width=0.45\textwidth]{plots/MP_t_LP.eps}\\
\includegraphics[width=0.45\textwidth]{plots/HP_t_LP.eps}
\includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
\caption{Transitions after the Lamperti transform. The transitions now present a normal Gaussian shape. This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
  \label{fig:LP_transitions}
\end{figure}
%---END SECTION 1---

@@

\subsection{Optimization} \label{opt_sec}
{\color{red} Rewrite the discussion to obtain fast initial estimate for the two unknow parameters.}

@@

\begin{equation}
\theta_0\approx\arg\min_{\theta} \sum\limits_{j}^M \sum\limits_i^N \left( v_{i+1,j}  - v_{i,j}- \left( - \theta_t v_{i,j}\right) \left(t_{i+1,j} - t_{i,j} \right)  \right)^2,
\label{inital_theta}
\end{equation}

@@

\begin{equation}
\theta_0 \alpha \approx \frac{1}{2M\Delta t} \sum\limits_j^M \frac{ \sum\limits_i^N (x_{i+1,j}  - x_{i,j})^2}{ \sum\limits_i^N x_{i,j}(1-x_{i,j}) } \,.
\end{equation}

@@

\begin{table}
\centering
\begin{tabular}{cccc}
\toprule
Model   &  parameters $(\theta_0, \alpha,\delta)$   & AIC & BIC \\ \midrule
Model 1 &  $(\add,\add) $    &  \add   &  \add   \\
Model 2 &   $(1.2,0.1,0.6)$   &  \add   &   \add    \\ 
\bottomrule
\end{tabular}
\caption{We compare the different models based on information criterion. \add }
\label{tab:model_comparison}
\end{table}
%---END SECTION 5---

%---BEGIN SECTION 6---
\section{Forecast Provider Comparison} \label{Section_6}
We compare forecasts from two different companies for the same period.
\begin{table}
\centering
\begin{tabular}{cccc}
\toprule
Forecast Provider & parameters $(\theta_0, \alpha,\delta)$ & AIC & BIC \\ \midrule
Provider A  &  $(\add,\add)$      &  \add   & \add    \\
Provider B  & $(\add,\add) $  &  \add   &   \add  \\ 
\bottomrule
\end{tabular}
\caption{\add}
\label{tab:forcast_comparison}
\end{table}
In Figure (\add)-(\add), we see that forecast provider A is of better quality than provider B. This is confirmed by both the AIC and BIC information criteria.

 \begin{table}[h]
 \centering
 \begin{tabular}{cccc}
 \toprule
 Model & parameters $(\theta_0, \alpha)$  \\
 \midrule
 \begin{tabular}[c]{@{}c@{}}low frequency data\\ (hourly)\end{tabular}               &  $(\add,\add) \pm (\add,\add)$   \\ 
 \begin{tabular}[c]{@{}c@{}}high frequency data\\  (every 10 minutes)\end{tabular} &  $(\add,\add) \pm (\add,\add)$      \\ \bottomrule
 \end{tabular}
 \caption{ \add confidence interval obtained using bootstrap}
 \label{tab:freq_comparison}
 \end{table}
%---END SECTION 6---

@@

\subsection{Initial guesses}

Following the instruction for the initial guesses from section $\ref{opt_sec}$, we get the initial guesses $(\theta_0,\alpha,\delta)\approx(1.2,0.1,0.6)$.

\begin{figure}[h!]
\centering
\includegraphics[width=0.6\textwidth]{plots/initial_guess/initial_theta_1.eps}
\caption{Value function from ($\ref{inital_theta}$) as a function of different $\theta_0$ values. We can observe that the function if flat for a wide range.}
\end{figure}

\subsection{Main guesses}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/1.eps}
\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/2.eps}\\
\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/3.eps}
\includegraphics[width=0.45\textwidth]{plots/paths_testing_days/4.eps}
\caption{We simulate following model 2  five possible future wind power production paths using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Forecast is from Uruguay pertaining to  year 2019.}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/1.eps}
\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/2.eps}\\
\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/3.eps}
\includegraphics[width=0.45\textwidth]{plots/bands_testing_days/4.eps}
\caption{{\color{red}Pending add legend and choose better colors.}We obtain confidence intervals following model 2  for future wind power production using the obtained optimal parameters $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Actual production plotted in retrospect. Forecast and data is from Uruguay pertaining to  year 2019.}
\end{figure}
%---END SECTION 7---
